---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getcommit

<!-- badges: start -->
<!-- badges: end -->

The goal of **getcommit** is to provide a simple interface for retrieving commit history from GitHub repositories and analyzing developer activity over time.  

With **getcommit**, you can:  
- Fetch recent commits from any public GitHub repository.  
- Filter commits by branch, date range, or number of commits.  
- Export commit history to a tidy data frame or CSV.  
- Visualize commit activity (e.g., by date, author, or time of day) in R.  

## Installation

You can install the development version of getcommit from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mahmudstat/getcommit")
```

## Examples

Let us see some commits from the `dplyr` package of the `tidyverse` ecosystem. 

```{r get_list}
library(getcommit)
comm <- get_commits("tidyverse/dplyr", n = 30, from = "2024-05-15", to = "2025-09-02")
head(comm)
```

## Commits by Mahedi Bhai

```{r mahedi}
library(getcommit)
comm <- get_commits("Mahedi-61/Mahedi-61.github.io", n = 25, from = "2021-01-11", to = "2025-09-02")
head(comm)
```

## Viewing the commits on the clockplot

```{r plot_list}
library(clockplot)
library(dplyr)
library(hms)
comm <- comm %>%
  mutate(hms = hms::as_hms(date))
# Step 2: Plot with clockplot
clock_chart_qlt(
  comm,
  time = hms,
  crit = author
)
```

